Neural Textures make Better Simulators ``I can't believe it's not real!"

### 2022-06-11 CORL/example.tex
Added some texture realism text

\subsection{Image Translation}

@@

\subsection{Unprojection Consistency Loss}
\label{unprojection_consistency_loss}

@@

To maintain surface consistency, we sample a random batch of UVL scenes $S\toB$, and translate them into $\ph\toB$.
Using geometric knowledge of the scene encoded in $S\toB$, we individually unproject each $\ph_i \in \ph\toB$ back into texture space, to obtain $B$ sets of $L$ unprojected textures $u\toBL$.
We then use the per-pixel, batch-wise standard deviation of the unprojections as unprojection consistency loss $\lUC = \sigma(u\toBL)\toL$.
This loss observes how badly these unprojections differ from one another, and thus how different the object surfaces appear between translations.

@@

This loss is a fairly intuitive and effective way to maintain surface consistency. There are some caveats to this loss, however.
In order to produce a standard deviation greater than $0$, we must have a batch size greater than $1$.
In fact, $\lUC$ is most useful with large batch sizes because observing the same surface in multiple elements of a batch becomes more likely as the batch size increases.
There is a limited number of elements we can fit into video memory, so environments that rarely show a particular region of a surface will rarely have $\lUC$ applied to that region.
In first-person environments, this might be more of a problem - particularly when exploring multiple rooms (a task we haven't done though - should I mention this?)

@@

>>>>

\subsection{Image Translation}
\label{sec:image_translation}

@@

\subsection{Unprojection Consistency Loss}
\label{sec:unprojection_consistency_loss}

@@

To maintain surface consistency, we sample a random batch of UVL scenes $S\toB$, and translate them into $\ph\toB$.
Using geometric knowledge of the scene encoded in $S\toB$, we individually unproject each $\ph_i \in \ph\toB$ back into texture space, to obtain $B$ sets of $L$ unprojected textures $u\toBL$.
We then use the per-pixel, batch-wise standard deviation of the unprojections as unprojection consistency loss $\lUC = \sigma(u\toBL)\toL$.
This loss observes how different these unprojections are from one another, and thus how different the object surfaces appear between translations.

@@

This loss is a fairly intuitive and effective way to maintain surface consistency. There are some caveats, however.
In order to produce a standard deviation greater than $0$, we must have a batch size greater than $1$.
Furthermore, environments that rarely show a particular region of a surface will rarely have $\lUC$ applied to that region because they're unlikely to show up twice in the same batch.
For this reason, $\lUC$ is most useful with large batch sizes.% because observing the same surface in multiple elements of a batch becomes more likely as the batch size increases.
But because video memory limits our batch sizes, first-person environments might be more of a challenge for $\lUC$ - particularly when exploring multiple rooms (a task we haven't done though - should I mention this?)

@@

We can improve the translation results by forcing the neural texture to look realistic, instead of allowing it to have arbitrary colors.

So far, we've taken an image translator $T$ and added neural textures $\tau$ and a surface consistency constraint $\lUC$. 
If we wanted to, could stop here - those formulations are sufficient to produce consistent sim-to-real translations.
However, we can improve this further.

Up until now we have not put any constraints on this neural texture. With only the above constraints, $\tau$ might look wildly different each time you train it.
As seen in the top row of figure \ref{fig:texture_realism_ablation}, the neural texture might not look anything like the translation results.

We introduce a new loss, called texture realism loss. $\lTR$ image similarity loss that encourages $\pi \approx \ph$.
In other words, $\lTR$ makes the neural texture more realistic by making the neural texture projections more realistic.
This loss forces the neural texture to approximate the albedo of the surfaces in a scene.
This image similarity loss is calculated the same way image similarity losses are calculated in section \ref{sec:image_translation}: L2 loss minus MSSSIM.
